PDBF Documentation

### 2015-08-06 pdbf-doc.tex
changed some filenames
replaced url to demo paper

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{PDBF}
\usepackage{wrapfig}
\usepackage[hidelinks]{hyperref}
\usepackage[a4paper,vmargin={20mm,40mm},hmargin={20mm,20mm}]{geometry}

@@

\noindent A \href{https://infosys.uni-saarland.de/publications/p1972-dittrich.pdf}{demo paper} of our tool is appearing at \href{http://www.vldb.org/2015/}{VLDB 2015}.

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{pdbf}
\usepackage{wrapfig}
\usepackage[hidelinks]{hyperref}
\usepackage[a4paper,vmargin={20mm,40mm},hmargin={20mm,20mm}]{geometry}

@@

\noindent A \href{https://infosys.uni-saarland.de/publications/p1972-dittrich.html}{demo paper} of our tool is appearing at \href{http://www.vldb.org/2015/}{VLDB 2015}.
